Software Citation Principles

### 2016-03-21 sc-principles/software-citation-principles.tex
adding "Appendix" before an Appendix number

With close to 50 working group participants (\ref{app:wg_members}) representing a range of research domains, the working group was tasked to
document existing practices in their respective communities. A total of 47 documents were submitted by working group
participants, with the life sciences, astrophysics, and geosciences being particularly well-represented in the submitted
resources.

>>>>

With close to 50 working group participants (see Appendix~\ref{app:wg_members}) representing a range of research domains, the working group was tasked to
document existing practices in their respective communities. A total of 47 documents were submitted by working group
participants, with the life sciences, astrophysics, and geosciences being particularly well-represented in the submitted
resources.
